Replicated designs based on Sobol' sequences to estimate main effects of model inputs

### 2016-05-11 crass/crass.tex
Minor changes
Changes in CRASS section 2

The introduction of digital nets and sequences has its origin in numerical integration and uniform distribution. Explicit constructions of digital nets and sequences have been developed notably by Sobol' and Niederreiter \cite{niderreiter} into the overarching notion of $(t,m,s)$-nets and $(t,s)$-sequences. A comprehensive theory of $(t,m,s)$-net and $(t,s)$-sequences was first formulate by Niederreiter.

$(t,m,s)$-nets are defined as point sets in $\cube$ whose quality is measured by the parameter $t$, called $t$-value. They are defined as follows:
\begin{definition}%[$(t,m,s)-net$]
Let $\mathcal{A}$ be the set of all elementary intervals $A\in\cube$ where $A=\prod_{j=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $s\geq 1$, $b\geq 2$, $\gamma_j\geq 0$, and $b^{\gamma_j}>\alpha_j\geq 0$. For $m\geq t\geq 0$, the point set $\mathcal{P}\in\cube$ with $b^m$ points is a $(t,m,s)-net$ in base $b$ if every $A$ with volume $b^{t-m}$ contains $b^t$ points of $\mathcal{P}$.
\end{definition}

A $(t,m,s)$-net is defined such that all elementary intervals of volume at least $b^{t-m}$ will enclose a proportional number of points. The most evenly spread nets are $(0,m,s)$-nets, since each elementary interval of the smallest volume possible, $b^{-m}$, contains exactly one point. %Note that if $t'>t$, $(t,m,s)$-nets are always $(t',m,s)$-nets.

$(t,s)$-sequences are the infinite analogues of $(t,m,s)$-nets. They are defined as follows:
\begin{definition}%[$(t,s)$-sequence]
For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i\in\mathbb{N}_0}$ is a $(t,s)$-sequence in base $b$, if for every set $\mathcal{P}_{\ell,m}=\{\vx_i\}_{i=\ell b^m}^{(\ell+1)b^m-1}$ with $\ell\geq 0$ and $m\geq t$, $\mathcal{P}_{\ell,m}$ is a $(t,m,s)$-net in base $b$.
\end{definition}
\bigskip

All $(t,m,s)$-nets and $(t,s)$-sequences relevant for applications are based on a digital construction scheme over a finite field $\mathbb{F}_b$ with $b$ a prime power number. Digital nets and sequences referred to these structures. 
\bigskip

>>>>

Digital nets and sequences were first introduced by Niederreiter \cite{SIAM92book} in the numerical integration framework to define good uniformly distributed points in $\cube$. They can also appear in the literature as digital $(t,m,s)$-nets and digital $(t,s)$-sequences, or simply $(t,m,s)$-nets and $(t,s)$-sequences. Sobol' \cite{Sobol} and Niederreiter-Xing sequences are two examples whose explicit constructions are detailed in \cite{Niederreiter, Sobol, DickPhilischammer,DickKritzer,KuoJoe}.

The quality of any $(t,m,s)$-net or $(t,s)$-sequence is measured by $t$, called the $t$-value. The $t$-value is introduced in the $(t,m,s)$-net definition as follows:

\begin{definition}%[$(t,m,s)-net$]
Let $\mathcal{A}$ be the set of all elementary intervals $A\in\cube$ where $A=\prod_{j=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $s\geq 1$, $b\geq 2$, $\gamma_j\geq 0$, and $b^{\gamma_j}>\alpha_j\geq 0$. For $m\geq t\geq 0$, the point set $\mathcal{P}\in\cube$ with $b^m$ points is a $(t,m,s)-net$ in base $b$ if every $A$ with volume $b^{t-m}$ contains $b^t$ points of $\mathcal{P}$.
\end{definition}

Thus, a $(t,m,s)$-net is defined such that all elementary intervals of volume at least $b^{t-m}$ will enclose a proportional number of points of $\mathcal{P}$, namely $b^{t-m}|\mathcal{P}|$ points. The most evenly spread nets are $(0,m,s)$-nets, since each elementary interval of the smallest volume possible, $b^{-m}$, contains exactly one point.

By increasing $m$, we increase the number of points of the $(t,m,s)$-net. If one considers the limit for $m\rightarrow\infty$, $(t,s)$-sequences are defined as:
\begin{definition}%[$(t,s)$-sequence]
For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i\in\mathbb{N}_0}$ is a $(t,s)$-sequence in base $b$, if for every set $\mathcal{P}_{\ell,m}=\{\vx_i\}_{i=\ell b^m}^{(\ell+1)b^m-1}$ with $\ell\geq 0$ and $m\geq t$, $\mathcal{P}_{\ell,m}$ is a $(t,m,s)$-net in base $b$.
\end{definition}
\bigskip

All $(t,m,s)$-nets and $(t,s)$-sequences relevant for applications are based on a digital construction scheme over a finite field $\mathbb{F}_b:=\{0,\dots,b-1\}$ with $b$ a prime power number. Digital nets and sequences referred to these structures. 
\bigskip
